\documentclass{article}
\usepackage{pronouns}

% Example document for pronouns package

\begin{document}


Examples from http://www.pronouns.failedslacker.com/

\set

\They\ run\s.

\They\ quickly run\s\ to the tree.

\They[2] \were[2], I must say, very fast.

I watch as \they[2] \are[2] hit by a tree.

\They[3] go\es[3] along.

\They[4]'\re[4] a good person.

Hello! Today I met a person who goes by Example. \They\ \have\ a wonderful personality. That smile of \theirs\ really makes me happy. I could talk to \them\ all day although \they\ do\es n't talk about \themself\ much. I wonder if \their\ day has been wonderful. I hope so!

\section{Alice in Wonderland}

\set
 Example was beginning to get very tired of sitting by \their[1] sister on the bank, and of having nothing to do: once or twice \they[1] had peeped into the book \they[2] \were[2] reading, but it had no pictures or conversations in it,``and what is the use of a book," thought Example ``without pictures or conversation?"

\set
So \they\ \were\ considering in \their\ own mind (as well as \they\ could, for the hot day made \them\ feel very sleepy and stupid), whether the pleasure of making a daisy-chain would be worth the trouble of getting up and picking the daisies, when suddenly a White Rabbit with pink eyes ran close by \them.

\set
There was nothing so VERY remarkable in that; nor did Example think it so VERY much out of the way to hear the Rabbit say to \themself[2], ``Oh dear! Oh dear! I shall be late!" (when \they\ thought it over afterwards, it occurred to \them\ that \they\ ought to have wondered at this, but at the time it all seemed quite natural); but when the Rabbit actually TOOK A WATCH OUT OF \their[2] WAISTCOAT-POCKET, and looked at it, and then hurried on, Example started to \their\ feet, for it flashed across \their\ mind that \they\ had never before seen a rabbit with either a waistcoat-pocket, or a watch to take out of it, and burning with curiosity, \they\ ran across the field after \them[2], and fortunately was just in time to see \them[2] pop down a large rabbit-hole under the hedge.

\set
In another moment down went Example after \them[2], never once considering how in the world \they\ \were\ to get out again.

\set
The rabbit-hole went straight on like a tunnel for some way, and then dipped suddenly down, so suddenly that Example had not a moment to think about stopping \themself\ before \they\ found \themself\ falling down a very deep well.

\set
Either the well was very deep, or \they\ fell very slowly, for \they\ had plenty of time as \they\ went down to look about \them\ and to wonder what was going to happen next. First, \they\ tried to look down and make out what \they\ \were\ coming to, but it was too dark to see anything; then \they\ looked at the sides of the well, and noticed that they were filled with cupboards and book-shelves; here and there \they\ saw maps and pictures hung upon pegs. \they\ took down a jar from one of the shelves as \they\ passed; it was labelled ``ORANGE MARMALADE", but to \their\ great disappointment it was empty: \they\ did not like to drop the jar for fear of killing somebody, so managed to put it into one of the cupboards as \they\ fell past it.

\set
``Well!" thought Example to \themself, ``after such a fall as this, I shall think nothing of tumbling down stairs! How brave they'll all think me at home! Why, I wouldn't say anything about it, even if I fell off the top of the house!" (Which was very likely true.)

~

``But I'm NOT a serpent, I tell you!" said Example . ``I'm a-I'm a-"

``Well! WHAT are you?" said the Pigeon. ``I can see you're trying to invent something!"

\set
``I-I'm a person," said Example, rather doubtfully, as \they\ remembered the number of changes \they\ had gone through that day.

``A likely story indeed!" said the Pigeon in a tone of the deepest contempt. ``I've seen a good many persons in my time, but never ONE with such a neck as that! No, no! You're a serpent; and there's no use denying it. I suppose you'll be telling me next that you never tasted an egg!"

``I HAVE tasted eggs, certainly," said Example, who was a very truthful child; ``but persons eat eggs quite as much as serpents do, you know."

\set
``I don't believe it," said the Pigeon; ``but if they do, why then they're a kind of serpent, that's all I can say."

\set
This was such a new idea to Example, that \they\ \were\ quite silent for a minute or two, which gave the Pigeon the opportunity of adding, ``You're looking for eggs, I know THAT well enough; and what does it matter to me whether you're a person or a serpent?"

\set
``It matters a good deal to ME," said Example hastily; 'but I'm not looking for eggs, as it happens; and if I was, I shouldn't want YOURS: I don't like them raw.'

\set
``Well, be off, then!" said the Pigeon in a sulky tone, as \they[2] settled down again into its nest. Example crouched down among the trees as well as \they\ could, for \their\ neck kept getting entangled among the branches, and every now and then \they\ had to stop and untwist it. After a while \they\ remembered that \they\ still held the pieces of mushroom in \their\ hands, and \they\ set to work very carefully, nibbling first at one and then at the other, and growing sometimes taller and sometimes shorter, until \they\ had succeeded in bringing \themself\ down to \their\ usual height.

~

\set
``Oh, I've had such a curious dream!" said Example, and \they\ told \their\ sister, as well as \they\ could remember them, all these strange Adventures of \theirs\ that you have just been reading about; and when \they\ had finished, \their\ sister kissed \them, and said, ``It WAS a curious dream, dear, certainly: but now run in to your tea; it's getting late." So Example got up and ran off, thinking while \they\ ran, as well \they\ might, what a wonderful dream it had been.

\end{document}